Multispecies survey specifications

### 2020-11-02 msSurveysTest.Rmd
fixing selectivity WIP

survObsBiom <- read_savedsurvs(d.name, 'survB')
age_comp_data <- read_savedsurvs(d.name, 'survAge')
len_comp_data <- read_savedsurvs(d.name, 'survLen')
wtage <- read_savedsurvs(d.name, 'survWtage')
annage_comp_data <- read_savedsurvs(d.name, 'survAnnAge')
annage_wtage <- read_savedsurvs(d.name, 'survAnnWtage')

@@

`msfishery_01.R` configures the fishery dependent data:

@@

Model boxes show where our survey works now. We are including boxes x...x in these surveys:
```{r NOBAmap}
knitr::include_graphics("images/NOBAboxes.png")
```

@@

```{r full-test, message=FALSE, warning=FALSE, eval=FALSE}

@@

>>>>

# add this paste0(d.name, "/mscensus1") and add option to name save directory in wrappers
survObsBiom <- read_savedsurvs(d.name, 'survB')
age_comp_data <- read_savedsurvs(d.name, 'survAge')
len_comp_data <- read_savedsurvs(d.name, 'survLen')
wtage <- read_savedsurvs(d.name, 'survWtage')
annage_comp_data <- read_savedsurvs(d.name, 'survAnnAge')
annage_wtage <- read_savedsurvs(d.name, 'survAnnWtage')

@@

`msfishery_01.R` configures the fishery dependent data, which has a higher observation error on the total catch and does not get biological sampling from all areas:

@@

Model boxes show where our survey works now. We are including boxes 1:8, 21, 23:31, 33, 39:44, 47:49 in these surveys, and in fishery comps sampling:

```{r NOBAmap}
knitr::include_graphics("visualization_Rmd/images/NOBAboxes.png")
```

@@

```{r full-test, message=FALSE, warning=FALSE}

@@

Diagnose failure of om_comps on annage data with new survey config file--selectivity function by 10 agecl instead of annual ages.

```{r}

# source(here("config/mssurvey_spring_01.R"))
# source(here("config/mssurvey_fall_01.R"))
# source(here("config/msfishery_01.R"))

usersurvey <- c(here("config/mssurvey_spring_01.R"), 
                here("config/mssurvey_fall_01.R"))

n_reps <- 1

if(!is.null(omlist_ss$truenumsage_ss)){
    #numbers based fishery independent survey for age and length comps
    #allows for mulitple surveys
    annage_comp_datas <- list()

    for (s in usersurvey)
    {
      source(s, local = TRUE)

      # same user specifications as indices
      survey_annageN <- atlantisom::create_survey(dat = omlist_ss$truenumsage_ss,
                                                  time = survtime,
                                                  species = survspp,
                                                  boxes = survboxes,
                                                  effic = surveffic,
                                                  selex = survselex)
      #Sample fish for age composition
      # if we want replicates for obs error this sample function will generate them
      annage_comp_data <- list()
      for(i in 1:n_reps){
        annage_comp_data[[i]] <- atlantisom::sample_fish(survey_annageN, surveffN)
      }

      # save survey annual age comps
      if(save){
        saveRDS(annage_comp_data, file.path(d.name, paste0(scenario.name, "_",
                                                           survey.name, "survObsFullAgeComp.rds")))
      }
      annage_comp_datas[[survey.name]] <- annage_comp_data
    }

}else{annage_comp_datas <- NULL}

#breaking at sample_fish; test:

dat <- survey_annageN
effN <- surveffN

    #sum over boxes and assume sampling occurs coastwide (the sampled boxes were already subset in create functions)
    dat2 <- aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time),sum)
    names(dat2) <- c("species","agecl","time","numAtAge")

    #TODO: Need error checking--SKG moved nn assignement of effN to inside y loop from outside
	  dat2$numAtAgeSamp <- NA
	  for(sp in unique(dat2$species)) {
	    for(y in unique(dat2$time)) {
	      nn <- effN[effN$species==sp,"effN"]
	      ind <- dat2$species == sp & dat2$time == y
	      totalNums <- sum(dat2[ind,]$numAtAge) #add na.rm to get totalNums for Greenland halibut

	      if(nn > totalNums) {
	        nn <- totalNums
	        message("effN is greater than total numbers available, so nEff set equal to ", nn," for species ",sp," and time ",y,"\n")
	      }
	      probs <- matrix(dat2[ind,]$numAtAge,nrow=1)
	      if(nn > 0){
	        dat2[ind,]$numAtAgeSamp <- rmultinom(1,nn,probs)[,1]
	      } else { # sample is 0 if probs vector all 0s, no fish that year
	        dat2[ind,]$numAtAgeSamp <- rep(0, length(probs))
	        message("total numAtAge ", nn,", assigning 0 sample for species ",sp," and time ",y,"\n")
	      }
	    }
	  }

# breaking at Greenland halibut, which has no fish in ages 11-20 in this survey

	  survey_annageN %>% filter(species %in% "Green_halibut") %>% group_by(agecl) %>% tally(atoutput)

	  # want the function to return 0 for missing ages
	  # probs statement returns NA for ages 11-20
